Phonetic Transcription by Untrained Annotators

### 2018-06-04 2018-itat-krompachy/paper.tex
more itat 2018 text

@@

@@

On the other hand, nearly a third of the cases show the wrong phonetic
representation. This is a serious problem on at least two levels: Firstly, it
shows that the forced aligner failed to catch the error. Secondly

>>>>

The talks can be seen as companions to Makoň's written works. Together they form
a unique, extensive, consistent systematization of the spiritual path tailored
to modern westerners and accessible primarily to Czech speakers. It draws
heavily on traditional Christian mysticism as well as ancient tradition of India
and China, adapting them for the present. The whole system can be seen as a
manual for entering the eternal life prior to the physical death.

Makoň points to the life of Jesus as depicted by the gospels as to perfect,
detailed manual for the path to eternal life usable by anybody. He corrects many
alleged mistakes in the official Catholic doctrine, although he sees its
tradition as a very useful and underestimated tool. I, the author of this paper,
would personally find it most interesting to be able to compare key Makoň's
postulates with official stance of the Church and its evolution in the last
decades.

@@

\subsection{Phoneme Set}

We use a subset of PACal\cite{nouza1997phonetic}. We shall also refer to
individual phonemes in this paper using the PACal notation. For reference,
Table~\ref{tab:phones} lists the phonemes used with their IPA notation.

\begin{table}[htpb]
\fontspec{DoulosSIL}
\begin{center}
\begin{tabular}{|l|l|l|l||l|l|l|l|}
\hline
IPA & PACal & common grapheme & IPA & PACal &  common grapheme \\
\hline
% TODO: IPA
a  & a   & a      &     ɱ  & mg  & tra\underline{m}vaj \\
aː & aa  & á      &     n  & n   & \underline{n}e \\
aʊ̯ & aw  & au     &     ŋ  & ng  & pa\underline{n}t \\
b  & b   & b      &     ɲ  & nj  & \v{n} \\
t͡s & c   & c      &     o  & o   & o \\
t͡ʃ & ch  & č      &     oː & oo  & ó \\
d  & d   & d      &     oʊ̯ & ow  & ou \\
ɟ  & dj  & \v{d}  &     p  & p   & p \\
d͡z & dz  & dz     &     r  & r   & r \\
d͡ʒ & dzh & dž     &     r̝̊  & rsh & t\underline{\v{r}}i \\
ɛ  & e   & e      &     r̝  & rzh & \underline{\v{r}}íz \\
ɛː & ee  & é      &     s  & s   & s \\
eʊ̯ & ew  & eu     &     ʃ  & sh  & š \\
f  & f   & f      &     t  & t   & t \\
g  & g   & g      &     c  & tj  & \v{t} \\
ɦ  & h   & h      &     ʊ  & u   & u \\
i  & i   & i      &     uː & uu  & ú, \r{u} \\
iː & ii  & í      &     v  & v   & v \\
j  & j   & j      &     x  & x   & ch \\
k  & k   & k      &     z  & z   & z \\
l  & l   & l      &     ʒ  & zh  & ž \\
m  & m   & \underline{m}ák
                  &        & sil & \\
   &     &        &        & sp  & \\
\hline
\end{tabular}
\caption{Phones used in transcription}\label{tab:phones}
\end{center}
\end{table}
\normalfont

@@

On the other hand, nearly a third of the cases show the wrong phonetic
representation. This is a serious problem on at least two levels: Firstly, it
shows that the forced aligner failed to catch the error. Secondly, it lets bad
examples into the training dataset.

One of the apparent reasons for this to happen is that the dynamic dictionary
only recognizes exact matches. We can see in one file, for example, all
occurrences of the form {\em Weinfurter} to have correct pronunciation while
{\em Weinfurterovi} a broken one.

Other factors likely include user carelessness or and ignorance, which is
exactly what our application is trying to compensate, but fails in these cases.

The cases with false orthographic form don't pose much of a problem. It can
harden searching for the term in question but performing a search for the
phonetic respelling or even automatically searching the pronunciation would
easily mitigate this.

\section{Conclusion}

\section*{Acknowledgments}

The research was supported by SVV project number 260 453.\\
\\
This work has been using language resources stored
and distributed  by the LINDAT/CLARIN project of the Ministry of Education,
Youth and Sports of the Czech Republic (project LM2015071).
